---
title: "Accessing the matchSCore2 datasets"
author:
- name: Federico Marini
  affiliation: 
  - &id1 Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), Mainz
  - Center for Thrombosis and Hemostasis (CTH), Mainz
  email: marinif@uni-mainz.de
author:
- name: Elisabetta Mereu
  affiliation: 
  - &id2 National Center for Genomic Analysis, Center for Genomic Regulation (CRG), Barcelona, Spain
  - Barcelona Institute of Science and Technology (BIST), Barcelona, Spain
  email: elisabetta.mereu@cnag.crg.eu

date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('HCAData')`"
output: 
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Accessing the matchSCore2 datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignettePackage{matchSCore2Data}
---

**Compiled date**: `r Sys.Date()`

**Last edited**: 2020-04-07

**License**: `r packageDescription("matchSCore2Data")[["License"]]`

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = FALSE,
  warning = FALSE,
  message = FALSE
)
```

# Introducing the `matchSCore2Data` package

The `r Biocpkg("matchSCore2Data")` package allows a direct access to the dataset generated by the matchSCore2 project for further processing in R and Bioconductor.
It does so by providing the datasets as `r Biocpkg("SingleCellExperiment")` objects, i.e. a format which is both efficient and very widely adopted throughout many existing Bioconductor workflows.

The datasets are otherwise available in other formats (also as raw data) at this link: TODO...

# Installing `matchSCore2Data`

The `r Biocpkg("matchSCore2Data")` package can be installed in the conventional way via `r CRANpkg("BiocManager")`.

```{r install, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("matchSCore2Data")
```



This package makes extensive use of the `r Biocpkg("HDF5Array")` package to avoid loading the entire data set in memory.
Instead, it stores the counts on disk as a HDF5 file, and loads subsets of the data into memory upon request.

# Loading `matchSCore2Data`

```{r loadpkg}
library("matchSCore2Data")
```

We use the `matchSCore2Data` function to download the relevant files from Bioconductor's `r Biocpkg("ExperimentHub")` web resource. 

# Explore `matchSCore2Data`

The datasets are provided in the form of a `SingleCellExperiment` object. 
A natural companion to this data structure is the `r Biocpkg("iSEE")` package, which can be used for interactive and reproducible data exploration.

Any analysis steps should be performed in advance before calling `iSEE`, and since these datasets can be quite big, the operations can be time consuming, and/or require a considerable amount of resources.

## Processing ...

## Exploring the dataset with `iSEE`

Once the processing steps above are done, we can call `iSEE` with the subsampled `SingleCellExperiment` object. 

```{r launchisee, eval=FALSE}
if (require(iSEE)) {
  iSEE(sce)
}
```

## Saving the processed object

# Session info {-}

```{r sessioninfo}
sessionInfo()
```
